General constraints on magic distillation protocols from statistical mechanics

### 2021-04-25 magic_paper.tex
probably scrap further state conversion comparisons with thauma max?

Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which can be defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log_2{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
\end{equation}
and can be calculated numerically via a semi-definite program.

@@

I include in~\cref{fig:test} the mana and max--thauma bounds for the purification of (a) Norrell states and (b) $T$ states.
\nick{Need to include numerical majorization curves to compare, extend noise range.}

\begin{figure}[h]
    \centering
    \subfigure[][]{%
    \label{fig:norrell}%
    \includegraphics[height=3cm]{figs/compare_norrell.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:tstate}%
    \includegraphics[height=3cm]{figs/compare_tstate.pdf}}
    \caption{\textbf{Bound comparison} 
    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification;
    }%
    \label{fig:test}
\end{figure}

>>>>

Similar upper bounds on distillation rates for qudits of odd prime dimension include the mana bound~\cite{cit:veitch} and the max--thauma bound~\cite{Wang_2020} which can be defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log_2{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
\end{equation}
and can be calculated numerically via a semi-definite program\footnote{Provided as supplemental material with~\cite{Wang_2020}}.

@@

I include in~\cref{fig:test} the mana and max--thauma bounds for the purification of (a) Norrell states and (b) $T$ states.
\nick{Delete this probably?}

\begin{figure}[h]
    \centering
    \subfigure[][]{%
    \label{fig:norrell}%
    \includegraphics[height=3cm]{figs/compare_norrell.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:tstate}%
    \includegraphics[height=3cm]{figs/compare_tstate.pdf}}
    \caption{\textbf{Bound comparison} 
    \subref{fig:norrell} Norrell state purification; \subref{fig:tstate} $T$ state purification; \nick{Delete this probably?}
    }%
    \label{fig:test}
\end{figure}
